|

### 2025-01-21 doc/paper.qmd
streamlined paper outline

The paper is structured into sections corresponding to Tasks 1–4, where each section presents the research design choices and assumptions, documents the replication steps, and analyzes the replication results. The concluding remarks are provided in @sec-conclusion.

@@

### Step 1: Pulling the Data and Managing the Database
This Assignment involves pulling data directly from the Audit Analytics database and preparing the data for further analysis from raw data to final output.

@@

### Step 2: Data Preparation {#sec-step2_preparation}
The raw Transparency Report dataset initially contained 13,385 observations, representing entries for the year 2021. To ensure consistency with @EC_Report_2024, the abbreviation 'GR' for Greece was replaced with 'EL' in the trans_report_auditor_state field, affecting 188 rows.

@@

### Step 3: Analysis Implementation and Figure Reproduction
The analysis step computes market concentration metrics for audit firms across EU countries and at the EU level using the prepared transparency data. The analysis begins by calculating the market shares of the Big 4, 10KAP, and CR4 audit firm groups for the number of statutory audits conducted in 2021. For each country, the Big 4 market share is derived as the percentage of PIE statutory audits conducted by Deloitte, EY, KPMG, and PwC, while the CR4 market share represents the top four audit firms in each country based on audit counts. The 10KAP market share includes the Big 4 along with six additional networks, providing a broader view of market concentration.

@@

>>>>

The paper is structured into sections corresponding to Tasks 1–3 (@sec-task1, @sec-task2, @sec-task3), each detailing the research design choices and assumptions, documenting the replication steps, and analyzing the replication results for the respective segment. @sec-task4 sketches the survey design as a non-archival study that allows evaluating the key findings of the seminal paper. The concluding remarks are provided in @sec-conclusion.

@@

  Step 1: Pulling the Data and Managing the Database
This Assignment involves pulling data directly from the Audit Analytics database and preparing the data for further analysis from raw data to final output.

@@

  Step 2: Data Preparation {#sec-step2_preparation}
The raw Transparency Report dataset initially contained 13,385 observations, representing entries for the year 2021. To ensure consistency with @EC_Report_2024, the abbreviation 'GR' for Greece was replaced with 'EL' in the trans_report_auditor_state field, affecting 188 rows.

@@

  Step 3: Analysis Implementation and Figure Reproduction
The analysis step computes market concentration metrics for audit firms across EU countries and at the EU level using the prepared transparency data. The analysis begins by calculating the market shares of the Big 4, 10KAP, and CR4 audit firm groups for the number of statutory audits conducted in 2021. For each country, the Big 4 market share is derived as the percentage of PIE statutory audits conducted by Deloitte, EY, KPMG, and PwC, while the CR4 market share represents the top four audit firms in each country based on audit counts. The 10KAP market share includes the Big 4 along with six additional networks, providing a broader view of market concentration.

@@

# Task 2 {#sec-task2}

# Task 3 {#sec-task3}

# Task 4 {#sec-task4}
